\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\setstretch{1.05}
\pagenumbering{gobble}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\begin{document}

{\Large \textbf{Yongkang Cheng}}\\[2pt]
\href{https://chengyongkang.me/}{chengyongkang.me} \;|\; 437-663-2855 \;|\; \href{mailto:iwmain@outlook.com}{iwmain@outlook.com} \;|\; \href{https://github.com/Ken-2511}{github.com/Ken-2511}

\today

\vspace{0.6em}
Dear Hiring Team,

I am a Computer Engineering student at the University of Toronto with a strong academic record and broad project experience across software, hardware, and AI. I am excited to apply for the 16-month Engineering Intern position at Tenstorrent.

What motivates me most about this opportunity is the chance to contribute to cutting-edge AI hardware while learning directly from experienced engineers across multiple domains. In my previous projects and internships, I have consistently taken on unfamiliar challenges—from FPGA design to deep learning applications—and quickly built the skills needed to deliver meaningful results. I thrive in environments where I can adapt, learn fast, and connect ideas across disciplines.

I believe this ability to learn rapidly and approach problems from different angles will allow me to make a strong contribution at Tenstorrent, even in areas that are initially new to me. I am eager to bring my curiosity, persistence, and collaborative mindset to your team and grow as an engineer in the process.

Thank you for considering my application. I look forward to the possibility of contributing to Tenstorrent’s mission and learning from your team.

Sincerely,

Yongkang Cheng
\end{document}

