\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\pagenumbering{gobble}

\geometry{margin=0.7in}
\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

\begin{document}

%------------------------------------------
% HEADER
%------------------------------------------
\begin{center}
    \huge \textbf{YONGKANG CHENG}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

%------------------------------------------
% EDUCATION
%------------------------------------------
\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op \\
\textit{GPA: 3.92/4.0 (Top 30 among first-year ECE students)} \\
Relevant Courses: Applied Fundamentals of Deep Learning, Software Design and Communication

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------
\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Programming:} Python, SQL, JavaScript/TypeScript, C++, Verilog
    \item \textbf{Frameworks:} FastAPI, Next.js, PyTorch
    \item \textbf{Tools:} Docker, Git, Nginx, Postgres, Linux, AWS
    \item \textbf{AI/ML:} LLM Integration, Data Engineering, Model Deployment
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% EXPERIENCE
%------------------------------------------
\section*{\textbf{EXPERIENCE}}

\textbf{Frontend Manager, Voluntrack.org (Non-Profit)} \hfill May 2024 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Managed a 4-person team to revamp the web interface using React.js, enhancing user experience.
    \item Conducted biweekly stand-ups, assigned tasks via GitHub Projects, improving team efficiency.
    \item Increased user engagement by 20\% with redesigned layouts and optimized user flows.
\end{itemize}

\textbf{Project Lead, Handwritten Text Recognition (University of Toronto)} \hfill Jun 2024 - Aug 2024
\begin{itemize}[leftmargin=0.2in]
    \item Developed a CRNN model in PyTorch achieving 87\% word-level accuracy on test sets.
    \item Implemented image segmentation algorithms for processing 1024$\times$1024 inputs in under 4 seconds.
    \item Designed training pipelines, processing over 10,000 samples efficiently.
\end{itemize}

\textbf{Project Manager, Wellness Room Expansion (University of Toronto)} \hfill Jan 2024 -- Apr 2024
\begin{itemize}[leftmargin=0.2in]
    \item Led a 6-person team to redesign a wellness room, presenting 3 finalized proposals based on 100+ ideas.
    \item Streamlined task tracking with Gantt charts, ensuring on-time completion of 100+ tasks.
    \item Created detailed 3D visualizations in Blender for stakeholder review, reducing iterations.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% PROJECTS
%------------------------------------------
\section*{\textbf{PROJECTS}}

\textbf{Diary with AI Feedback} \hfill Sep 2023 -- Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a journaling platform integrated with OpenAI GPT API to analyze and provide feedback on user entries.
    \item Reduced API call costs to under \$0.2 per request while maintaining fast response times.
\end{itemize}

\textbf{Verilog Pac-Man Game (University of Toronto)} \hfill Nov 2024
\begin{itemize}[leftmargin=0.2in]
    \item Developed a VGA-compatible Pac-Man game on FPGA, debugging state-machine logic for stability.
    \item Used Python for automated sprite generation, enabling seamless graphics integration.
\end{itemize}

\textbf{WillPower: Time Management System} \hfill Jan 2025 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Created a modular system for behavior tracking using Raspberry Pi, FastAPI, and Nginx.
    \item Currently exploring transfer learning and Azure Face API for data analysis on over 20,000 images.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% AWARDS & ACCOMPLISHMENTS
%------------------------------------------
\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for academic excellence (GPA 3.92/4.0).
\end{itemize}

\textbf{American Computer Science League (ACSL) - Bronze Prize} \hfill Jan 2021
\begin{itemize}[leftmargin=0.2in]
    \item Placed in top 10\% overall after 60+ hours of rigorous training.
\end{itemize}

\end{document}
