\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem} % 避免 ulem 修改默认的 LaTeX 行为
% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble} % 取消页码

\geometry{margin=0.7in}

\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

% @ChatGPT: IMPORTANT INFORMATION: this is the master resume. You may be prompted to modify this file based on the job you are applying for.
% For each job application, you should write a new file by COPYING most of the content from this file.
% You are NOT allowed to change the content unless you are prompted by another `@ChatGPT' message.
% You need to delete two or three of the projects, experiences, or awards that are less relevant to the job you are applying for so as to make the resume fit within one page.
% You should not change any of the formatting, including `\geometry...` and `\noindent...' etc.

\begin{document}

%------------------------------------------
% HEADER
%------------------------------------------
\begin{center}
    \huge \textbf{YONGKANG CHENG}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

%------------------------------------------
% EDUCATION
%------------------------------------------
\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op \\
\textit{GPA: 3.92/4.0 (Top 30 among first-year ECE students)} \\
Relevant Courses: Applied Fundamentals of Deep Learning, Software Design and Communication

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------
% @ChatGPT: when you are modifying this section, you may want to remove some of the skills that are less relevant to the job you are applying for.
\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Programming:} Python, C/C++, JavaScript/TypeScript, Java, Verilog, Assembly
    \item \textbf{Frameworks:} PyTorch, React, FastAPI
    \item \textbf{Tools:} Linux, SQL/NoSQL, Nginx, Docker, Git, SSH
    \item \textbf{Hardware:} Arduino, Raspberry Pi, FPGA, LTSpice, Quartus, ModelSim
    \item \textbf{Data and Visualization:} NumPy, Pandas, Matplotlib
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% EXPERIENCE
%------------------------------------------
\section*{\textbf{EXPERIENCE}}
% add links

\noindent\href{https://github.com/VolunTrack/Web}{\uline{
\textbf{Frontend Manager, Voluntrack.org (Non-Profit)}}} \hfill May 2024 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Coordinated a 4-person frontend team using React.js to renew the web interface.
    \item Conducted biweekly stand-ups, assigned tasks in GitHub Projects, and streamlined communication in the team.
    \item Improved user engagement by approximately 20\% through enhanced app layouts and intuitive user flows.
    \item Utilized Figma for UI design and MS Project to keep track of tasks and deadlines.
\end{itemize}

\vspace{0.3cm}
\noindent\href{https://github.com/Ken-2511/HandwritingRecognition}{\uline{
\textbf{Project Lead, Handwritten Text Recognition (University of Toronto)}}} \hfill Jun 2024 - Aug 2024
\begin{itemize}[leftmargin=0.2in]
    \item Led a remote team to develop a PyTorch-based CRNN model for handwritten text recognition.
    \item Achieved 87\% word-level and 95\% character-level accuracy on the test set with 10,000+ samples.
    \item Deployed connected-pixel algorithms for word positioning and word segmentation, processing 1024$\times$1024 images in less than 4 seconds.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% PROJECTS
%------------------------------------------
\section*{\textbf{PROJECTS}}

\noindent\href{https://github.com/Ken-2511/Diary-with-ChatGPT-Comment}{\uline{
\textbf{Diary with AI Feedback}}} \hfill Sep 2023 -- On Going
\begin{itemize}[leftmargin=0.2in]
    \item Designed and implemented a journaling program integrated with OpenAI’s GPT API, generating insightful feedback and suggestions for over 570 diary entries.
    \item Developed a diary sorting algorithm to retrieve contextually similar past entries, enhancing user experience and maintaining API costs below 0.2\$ per call.
    \item Optimized data-sorting pipelines and API request processes, reducing average diary load time from 10s to 0.5s, enabling seamless daily use.
\end{itemize}


\vspace{0.3cm}
\noindent\href{https://github.com/Ken-2511/ECE241-Project}{\uline{
\textbf{Verilog Pac-Man Game (University of Toronto)}}} \hfill Nov 2024
\begin{itemize}[leftmargin=0.2in]
    \item Created a Pac-Man-style FPGA game using Verilog supporting PS/2 keyboard input and VGA output.
    \item Debugged signal synchronization issues and state-machine logic, boosting overall stability and playability.
    \item Automated image conversion using Python + OpenCV for seamless integration of game graphics.
    \item Prototypeed the game using Pygame, ensuring accurate emulation of the FPGA version for agile development.
\end{itemize}

\vspace{0.3cm}
\noindent\href{https://chengyongkang.me/chat}{\uline{
\textbf{Self-Clone Chatbot with Diary Database}}} \hfill Oct 2024 - Present
% @ChatGPT: for this project, if the job doesn't have so much related technical skills, you can remove this project.
\begin{itemize}[leftmargin=0.2in]
    \item Built a self-hosted AI-powered chatbot that replicates personal interaction styles, deployed using React.js, FastAPI, and Nginx on a Raspberry Pi.
    \item Integrated OpenAI API and a NoSQL database for real-time Q\&A functionality with personal diary data.
    \item Ensured secure and seamless remote access by implementing TLS encryption, DDNS, and optimizing for daily traffic from personal networks.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% AWARDS & ACCOMPLISHMENTS
%------------------------------------------
\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\noindent\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for outstanding academic performance (GPA 3.92/4.0).
\end{itemize}


\end{document}
