\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\pagenumbering{gobble}
\geometry{margin=0.7in}
\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

\begin{document}

\begin{center}
    \huge \textbf{YONGKANG CHENG}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op \\
\textit{GPA: 3.92/4.0 (Top 30 among first-year ECE students)} \\
Relevant Courses: Applied Fundamentals of Deep Learning, Software Design and Communication

\noindent\rule{\linewidth}{1pt}

\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Programming:} Python, C/C++, JavaScript/TypeScript, SQL
    \item \textbf{Tools:} Docker, Git, Linux, FastAPI, Nginx
    \item \textbf{Data and Visualization:} Pandas, NumPy, Matplotlib
    \item \textbf{Version Control:} GitHub, GitLab
\end{itemize}

\noindent\rule{\linewidth}{1pt}

\section*{\textbf{EXPERIENCE}}

\noindent\href{https://github.com/VolunTrack/Web}{\uline{\textbf{Frontend Manager, Voluntrack.org (Non-Profit)}}} \hfill May 2024 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Coordinated a 4-person frontend team using React.js to renew the web interface.
    \item Conducted biweekly stand-ups, assigned tasks in GitHub Projects, and streamlined communication in the team.
    \item Improved user engagement by approximately 20\% through enhanced app layouts and intuitive user flows.
\end{itemize}

\vspace{0.3cm}
\noindent\href{https://github.com/Ken-2511/HandwritingRecognition}{\uline{\textbf{Project Lead, Handwritten Text Recognition (University of Toronto)}}} \hfill Jun 2024 - Aug 2024
\begin{itemize}[leftmargin=0.2in]
    \item Led a remote team to develop a PyTorch-based CRNN model for handwritten text recognition.
    \item Deployed connected-pixel algorithms for word positioning and word segmentation, processing 1024$\times$1024 images in under 4 seconds.
    \item Achieved 87\% word-level and 95\% character-level accuracy on a 10,000+ sample dataset.
\end{itemize}

\vspace{0.3cm}
\noindent\href{https://github.com/Ken-2511/WillPower}{\uline{\textbf{WillPower \textbar{} Time Management \& Monitoring}}} \hfill Jan 2025 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a modular system with Raspberry Pi capturing images and sending them to a Windows host for analysis.
    \item Deployed Nginx, FastAPI, and Jenkins pipelines for seamless CI/CD and system integration.
    \item Designed data-sorting algorithms to enhance real-time monitoring capabilities and analysis efficiency.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

\section*{\textbf{PROJECTS}}

\noindent\href{https://chengyongkang.me/chat}{\uline{\textbf{Self-Clone Chatbot with Diary Database}}} \hfill Oct 2024 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a self-hosted AI-powered chatbot using React.js, FastAPI, and Nginx on a Raspberry Pi.
    \item Integrated OpenAI API and a NoSQL database for real-time Q\&A functionality with personal diary data.
    \item Ensured secure and seamless remote access by implementing TLS encryption and DDNS.
\end{itemize}

\vspace{0.3cm}
\noindent\href{https://github.com/Ken-2511/RainBirthdayGift}{\uline{\textbf{RainBirthdayGift \textbar{} AI-Driven Chatbot}}} \hfill Apr 2024
\begin{itemize}[leftmargin=0.2in]
    \item Built a GPT-4-powered chatbot in 3 days using C\#, .NET, and WPF framework.
    \item Enhanced responsiveness with asynchronous API calls and optimized user interaction flows.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\noindent\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for outstanding academic performance (GPA 3.92/4.0).
\end{itemize}

\vspace{0.3cm}
\noindent\textbf{American Computer Science League (ACSL) - Bronze Prize} \hfill Jan 2021
\begin{itemize}[leftmargin=0.2in]
    \item Placed in top 10\% overall, with top-20\% scores in the 4th round, after 60 hours of training.
\end{itemize}

\end{document}
