\documentclass[letterpaper,10pt]{article}
\usepackage{geometry}
\geometry{margin=0.7in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\pagenumbering{gobble}

\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

\begin{document}

%------------------------------------------
% HEADER
%------------------------------------------
\begin{center}
    \huge \textbf{Yongkang Cheng}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

%------------------------------------------
% EDUCATION
%------------------------------------------
\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op (cGPA: 3.87/4.0) \\
Relevant Courses: Digital Logic Design, Computer Architecture, Real-Time Systems, Signal Processing

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------
\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Embedded Programming:} C/C++, Assembly (RISC-V, ARM), Python, Real-time Programming
    \item \textbf{Hardware Platforms:} FPGA (Intel DE1-SoC), STM32, Arduino, Raspberry Pi, Nios-V, ARM Cortex
    \item \textbf{Hardware Design:} Verilog, PCB Design, Circuit Analysis, Digital Signal Processing
    \item \textbf{Tools \& Protocols:} Quartus, ModelSim, Git, I2C, SPI, UART, CAN, GPIO, PWM, ADC/DAC
    \item \textbf{Robotics \& Control:} PID Control, Sensor Integration, Motor Control, Computer Vision
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% EXPERIENCE
%------------------------------------------
\section*{\textbf{EXPERIENCE}}

\noindent\textbf{Research Assistant, Wireless Power Transfer Coil Design (University of Toronto)} \hfill Jul 2025 - Aug 2025\\
\textit{Research Intern, X-Lab, University of Toronto} \hfill \textit{Toronto, ON}
\begin{itemize}[leftmargin=0.2in]
    \item Designed 13.56MHz WPT coils for a BCI implant (3mm×8mm RX, \textasciitilde20mm link).
    \item Ran HFSS sweeps (turns, trace size, TX diameter) to quantify impacts on coupling ($k$) and quality factor ($Q$).
    \item Produced PCB layouts with tuning plan; distilled design rules and prepared prototypes for validation.
    \item Implemented embedded control systems for power regulation and wireless communication protocols.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/ppm-psk-visualize}
{\uline{\textbf{Research Assistant, Ultra-Wideband Receiver Design (University of Toronto)}}} \hfill Jun 2025 - Jul 2025\\
\textit{Research Intern, X-Lab, University of Toronto} \hfill \textit{Toronto, ON}
\begin{itemize}[leftmargin=0.2in]
    \item Verified hybrid PPM+PSK TX chip pre tape-out; built embedded signal processing systems for 2ns symbol sync.
	\item Implemented real-time pulse-position detection algorithms on embedded processors with sub-microsecond latency.
    \item Developed low-level drivers and interrupt handlers for high-speed data acquisition systems.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% PROJECTS
%------------------------------------------
\section*{\textbf{PROJECTS}}

\noindent\href{https://github.com/alexzjm/ece243-sound-synthesizer}{\uline{
\textbf{FPGA Polyphonic Synthesizer (DE1‑SoC)}}} \hfill Mar 2025
\begin{itemize}[leftmargin=0.2in]
    \item Implemented a 20‑voice digital synthesizer in C for a Nios‑V soft‑core, streaming \textbf{8 kHz Q15 audio} through the on‑chip Audio FIFO.  
    \item Replaced all floating‑point math with \textbf{32‑bit phase accumulators} and fixed‑point kernels for real‑time audio processing.  
    \item Designed an \textbf{ADSR envelope engine} with hardware-software co-design; integrated slide‑switch GPIO and pushbutton interrupts.
    \item Integrated PS/2 keyboard interrupts for sub‑µs latency note‑on/off events with real-time response guarantees.
    \item Built custom VGA display controller with double‑buffered 320 × 240 output and modular drawing primitives for live waveform visualization.
    \item Implemented efficient memory management and DMA transfers for seamless audio streaming without buffer underruns.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/ECE241-Project}{\uline{
\textbf{Verilog Pac-Man Game (University of Toronto)}}} \hfill Nov 2024
\begin{itemize}[leftmargin=0.2in]
    \item Created a Pac-Man-style FPGA game using Verilog supporting PS/2 keyboard input and VGA output.
    \item Implemented complex finite state machines for game logic, collision detection, and real-time sprite rendering.
    \item Designed custom memory controllers and video timing generators for stable 60Hz VGA output.
    \item Debugged signal synchronization issues and clock domain crossing problems for robust embedded system operation.
    \item Integrated embedded image processing pipeline with Python + OpenCV for graphics conversion and optimization.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/Photogate}{\uline{
\textbf{Photogate Speed Measurement System}}} \hfill High School Project
\begin{itemize}[leftmargin=0.2in]
    \item Designed and built 10 laser-based speed measurement units with 7-segment displays for high school physics education.
    \item Achieved sub-150us measurement precision using Arduino microcontrollers with interrupt-driven timing algorithms.
    \item Developed custom infrared communication protocol supporting 32-byte data transmission with error correction.
    \item Implemented precise timing circuits with crystal oscillators and hardware timer peripherals for accurate measurements.
    \item Created Python GUI using Tkinter for experiment control, real-time monitoring, and USB serial communication.
    \item Integrated 3D printed mechanical components with embedded electronics for durable classroom-ready construction.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/WillPower}{\uline{
\textbf{WillPower \textbar{} Time Management \& Monitoring}}} \hfill Jan 2025 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a distributed embedded system with Raspberry Pi capturing images and transmitting to Windows host for analysis.
    \item Implemented real-time data acquisition with camera interfacing, GPIO control, and network communication protocols.
    \item Deployed embedded web server using Nginx and FastAPI for RESTful API communication between distributed nodes.
    \item Developed low-power operation modes and efficient data compression algorithms for continuous monitoring applications.
    \item Created robust error handling and watchdog systems for autonomous embedded operation with minimal supervision.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{Autonomous Robot Navigation System} \hfill Academic Project
\begin{itemize}[leftmargin=0.2in]
    \item Developed autonomous navigation system using STM32 microcontroller with sensor fusion algorithms.
    \item Implemented PID control systems for motor control and path following with real-time feedback control.
    \item Integrated ultrasonic sensors, IMU, and encoders for obstacle avoidance and localization.
    \item Built custom PCB with power management, motor drivers, and sensor interface circuits.
    \item Programmed embedded C firmware with FreeRTOS for real-time task scheduling and interrupt handling.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{IoT Environmental Monitoring Station} \hfill Personal Project
\begin{itemize}[leftmargin=0.2in]
    \item Designed wireless sensor network using ESP32 microcontrollers for environmental data collection.
    \item Implemented low-power wireless communication protocols (WiFi, Bluetooth) for remote data transmission.
    \item Integrated multiple sensors (temperature, humidity, air quality) with calibration and filtering algorithms.
    \item Developed embedded web interface for real-time monitoring and historical data visualization.
    \item Created battery management system with solar charging capability for outdoor deployment.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{Digital Signal Processing on Embedded Systems} \hfill Academic Project
\begin{itemize}[leftmargin=0.2in]
    \item Implemented real-time FIR and IIR filters on ARM Cortex-M processors for audio signal processing.
    \item Optimized fixed-point arithmetic algorithms for embedded processors without floating-point units.
    \item Developed efficient circular buffer implementations and DMA-based data transfer for continuous processing.
    \item Created comprehensive testing framework with signal generators and automated verification systems.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/XiuShw/Wrong-Tree}{\uline{
\textbf{Core AI Developer, Wrong-Tree Unity Game}}} \hfill Dec 2024 - Jan 2025
\begin{itemize}[leftmargin=0.2in]
    \item Designed 9-state finite state machine for intelligent NPC behaviors with real-time decision-making algorithms.
    \item Implemented efficient proximity detection and dynamic reputation scoring systems optimized for embedded-style constraints.
    \item Created modular utility systems including random walk algorithms and distance-based targeting for resource-constrained environments.
    \item Built scalable multi-agent interaction framework supporting simultaneous operations with minimal computational overhead.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{City Mapify – Interactive City Mapping Application (University of Toronto)} \hfill Jan 2025 - Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Developed high-performance mapping engine in C++ optimized for embedded and resource-constrained systems.
    \item Designed efficient spatial data structures (\textbf{quadtrees}) for real-time querying with minimal memory footprint.
    \item Implemented pathfinding algorithms (\textbf{Dijkstra, A*}) optimized for embedded processors with limited computational resources.
    \item Enhanced performance with multithreading techniques suitable for multi-core embedded architectures.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% AWARDS & ACCOMPLISHMENTS
%------------------------------------------
\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\noindent\textbf{University of Toronto Excellence Award (UTEA)} \hfill Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Awarded UTEA for top academic performance and research potential in embedded systems.
    \item Completed a 14-week full-time research project focusing on embedded hardware design and implementation.
    \item Received \$7,500 scholarship for research excellence and inclusion.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for outstanding academic performance in embedded systems and computer engineering courses.
\end{itemize}

\end{document}