\documentclass[letterpaper,10pt]{article}
\usepackage{geometry}
\geometry{margin=0.7in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\pagenumbering{gobble}

\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

\begin{document}

%------------------------------------------
% HEADER
%------------------------------------------
\begin{center}
    \huge \textbf{Yongkang Cheng}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

%------------------------------------------
% EDUCATION
%------------------------------------------
\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op (cGPA: 3.87/4.0) \\
Relevant Courses: Digital Logic Design, Circuit Analysis, Signal Processing, Computer Architecture

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------
\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Hardware Design:} Verilog, VHDL, SystemVerilog, Digital Circuit Design, ASIC Design Flow
    \item \textbf{EDA Tools:} Quartus, ModelSim, LTSpice, HFSS, Cadence, Synopsys (familiar)
    \item \textbf{FPGA \& Processors:} Intel DE1-SoC, Nios-V, Altera/Intel FPGAs, ARM Cortex
    \item \textbf{Programming:} C/C++, Python, Assembly (RISC-V), MATLAB/Simulink
    \item \textbf{Hardware Tools:} Oscilloscope, Logic Analyzer, PCB Design, RF Testing Equipment
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% EXPERIENCE
%------------------------------------------
\section*{\textbf{EXPERIENCE}}

\noindent\href{https://github.com/Ken-2511/ppm-psk-visualize}
{\uline{\textbf{Research Assistant, Ultra-Wideband Receiver Design (University of Toronto)}}} \hfill Jun 2025 - Jul 2025\\
\textit{Research Intern, X-Lab, University of Toronto} \hfill \textit{Toronto, ON}
\begin{itemize}[leftmargin=0.2in]
    \item Verified hybrid PPM+PSK TX chip pre tape-out; built Python/Simulink pipelines for 2ns symbol sync and carrier recovery under discontinuous 4GHz.
	\item Built pulse-position detection and K-means cluster calibration to mitigate cross-modulation 100ps timing shifts.
    \item Developed comprehensive verification testbenches and signal integrity analysis for high-speed digital communications.
    \item Presented at Undergraduate Engineering Research Day with an interactive hybrid-modulation demo site.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{Research Assistant, Wireless Power Transfer Coil Design (University of Toronto)} \hfill Jul 2025 - Aug 2025\\
\textit{Research Intern, X-Lab, University of Toronto} \hfill \textit{Toronto, ON}
\begin{itemize}[leftmargin=0.2in]
    \item Designed 13.56MHz WPT coils for a BCI implant (3mm×8mm RX, \textasciitilde20mm link).
    \item Ran HFSS sweeps (turns, trace size, TX diameter) to quantify impacts on coupling ($k$) and quality factor ($Q$).
    \item Produced PCB layouts with tuning plan; distilled design rules and prepared prototypes for validation.
    \item Performed electromagnetic field simulations and impedance matching optimization for maximum power transfer efficiency.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% PROJECTS
%------------------------------------------
\section*{\textbf{PROJECTS}}

\noindent\href{https://github.com/alexzjm/ece243-sound-synthesizer}{\uline{
\textbf{FPGA Polyphonic Synthesizer (DE1‑SoC)}}} \hfill Mar 2025
\begin{itemize}[leftmargin=0.2in]
    \item Implemented a 20‑voice digital synthesizer in C for a Nios‑V soft‑core, streaming \textbf{8 kHz Q15 audio} through the on‑chip Audio FIFO.  
    \item Replaced all floating‑point math with \textbf{32‑bit phase accumulators} and fixed‑point kernels for sine, square, triangle, and sawtooth waves, enabling real‑time mixing and envelope processing.  
    \item Designed an \textbf{ADSR envelope engine} driven by slide‑switch "knobs" and pushbuttons; state changes are visualized on a double‑buffered 320 × 240 VGA UI.  
    \item Integrated PS/2 keyboard interrupts for sub‑µs latency note‑on/off events; on‑screen piano keys light up in sync with hardware playback.  
    \item Built modular drawing primitives (Bresenham, bitmap blits) to render live waveforms and icons; architecture supports future effects or MIDI input with minimal refactor.  
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/ECE241-Project}{\uline{
\textbf{Verilog Pac-Man Game (University of Toronto)}}} \hfill Nov 2024
\begin{itemize}[leftmargin=0.2in]
    \item Created a Pac-Man-style FPGA game using Verilog supporting PS/2 keyboard input and VGA output.
    \item Implemented complex finite state machines for game logic, sprite rendering, and collision detection.
    \item Debugged signal synchronization issues and state-machine logic, boosting overall stability and playability.
    \item Designed custom VGA controller with pixel-perfect timing and double-buffering for smooth animation.
    \item Automated image conversion using Python + OpenCV for seamless integration of game graphics.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/Photogate}{\uline{
\textbf{Photogate Speed Measurement System}}} \hfill High School Project
\begin{itemize}[leftmargin=0.2in]
    \item Designed and built 10 laser-based speed measurement units with 7-segment displays for high school physics education.
    \item Achieved sub-150us measurement precision using Arduino microcontrollers and custom PCB design.
    \item Developed custom infrared communication protocol supporting 32-byte data transmission for wireless control.
    \item Implemented precise timing circuits with crystal oscillators and interrupt-driven measurement algorithms.
    \item Integrated 3D printed components and aluminum framework for durable classroom-ready construction.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{Digital Signal Processing on FPGA} \hfill Academic Project
\begin{itemize}[leftmargin=0.2in]
    \item Implemented real-time FIR and IIR filters in Verilog for audio signal processing applications.
    \item Designed pipelined multiplier architectures to achieve high-throughput signal processing at 100MHz+.
    \item Developed comprehensive testbenches with automated verification using SystemVerilog assertions.
    \item Optimized resource utilization achieving 85\% LUT efficiency while meeting timing constraints.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{RF Circuit Analysis and Design} \hfill Academic Project
\begin{itemize}[leftmargin=0.2in]
    \item Designed and simulated low-noise amplifiers and voltage-controlled oscillators using LTSpice.
    \item Performed S-parameter analysis and stability analysis for multi-stage amplifier designs.
    \item Implemented impedance matching networks for maximum power transfer in RF applications.
    \item Conducted Monte Carlo analysis for process variation tolerance and yield optimization.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/XiuShw/Wrong-Tree}{\uline{
\textbf{Core AI Developer, Wrong-Tree Unity Game}}} \hfill Dec 2024 - Jan 2025
\begin{itemize}[leftmargin=0.2in]
    \item Designed 9-state finite state machine (Idle, Wander, Share, Steal, Flee) for intelligent NPC behaviors in Unity.
    \item Implemented AI decision-making algorithms with proximity detection and dynamic reputation scoring.
    \item Created multi-NPC interaction framework supporting simultaneous share/steal operations with visual feedback animations.
    \item Built modular utility systems including random walk algorithms and distance-based targeting for scalable codebase.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{City Mapify – Interactive City Mapping Application (University of Toronto)} \hfill Jan 2025 - Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Developed a high-performance mapping engine in C++ to process OpenStreetMap data and render city maps.
    \item Designed efficient spatial data structures (\textbf{quadtrees}) for dynamic querying and smooth zoom-based rendering.
    \item Implemented advanced pathfinding algorithms (\textbf{Dijkstra, A*}) for route planning and optimization.
    \item Enhanced performance with multithreading (OpenMP) for parallel processing of large datasets.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% AWARDS & ACCOMPLISHMENTS
%------------------------------------------
\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\noindent\textbf{University of Toronto Excellence Award (UTEA)} \hfill Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Awarded UTEA for top academic performance and research potential.
    \item Completed a 14-week full-time research project with faculty supervision.
    \item Received \$7,500 scholarship for research excellence and inclusion.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for outstanding academic performance in Electrical and Computer Engineering.
\end{itemize}

\end{document}