\documentclass[letterpaper,10pt]{article}
\usepackage{geometry}
\geometry{margin=0.7in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\pagenumbering{gobble}

\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

\begin{document}

%------------------------------------------
% HEADER
%------------------------------------------
\begin{center}
    \huge \textbf{Yongkang Cheng}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

%------------------------------------------
% EDUCATION
%------------------------------------------
\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op (cGPA: 3.87/4.0) \\
Relevant Courses: Applied Fundamentals of Deep Learning, Signal Processing, Linear Algebra, Statistics

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------
\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Machine Learning:} PyTorch, TensorFlow, Scikit-learn, OpenCV, CRNN, CNN, RNN, Transfer Learning
    \item \textbf{AI \& Data:} LangChain, OpenAI API, NumPy, Pandas, Matplotlib, Vector Search, NLP
    \item \textbf{Programming:} Python, C/C++, MATLAB/Simulink, R, SQL
    \item \textbf{Cloud \& Tools:} Azure Face APIs, Docker, Git, Jupyter, Google Colab, Linux
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% EXPERIENCE
%------------------------------------------
\section*{\textbf{EXPERIENCE}}

\noindent\href{https://github.com/Ken-2511/ppm-psk-visualize}
{\uline{\textbf{Research Assistant, Ultra-Wideband Receiver Design (University of Toronto)}}} \hfill Jun 2025 - Jul 2025\\
\textit{Research Intern, X-Lab, University of Toronto} \hfill \textit{Toronto, ON}
\begin{itemize}[leftmargin=0.2in]
    \item Built Python/Simulink pipelines for 2ns symbol sync and carrier recovery under discontinuous 4GHz signals.
	\item Implemented K-means clustering algorithms for calibration to mitigate cross-modulation 100ps timing shifts.
    \item Developed signal processing algorithms for pulse-position detection with sub-nanosecond precision.
    \item Presented at Undergraduate Engineering Research Day with an interactive machine learning demo site.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% PROJECTS
%------------------------------------------
\section*{\textbf{PROJECTS}}

\noindent\href{https://github.com/Ken-2511/HandwritingRecognition}{\uline{
\textbf{Project Lead, Handwritten Text Recognition (University of Toronto)}}} \hfill Jun 2024 - Aug 2024
\begin{itemize}[leftmargin=0.2in]
    \item Led a remote team to develop a PyTorch-based CRNN model for handwritten text recognition.
    \item Achieved 87\% word-level and 95\% character-level accuracy on the test set with 10,000+ samples.
    \item Implemented data augmentation techniques and regularization strategies to improve model generalization.
    \item Deployed connected-pixel algorithms for word positioning and word segmentation, processing 1024$\times$1024 images in less than 4 seconds.
    \item Optimized model architecture with attention mechanisms and bidirectional LSTM layers for sequence modeling.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/WillPower}{\uline{
\textbf{WillPower \textbar{} Time Management \& Monitoring}}} \hfill Jan 2025 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a modular system with Raspberry Pi capturing images and sending them to a Windows host for local storage and analysis.
    \item Deployed computer vision pipelines for real-time user monitoring and behavior analysis.
    \item Currently exploring Azure Face APIs and transfer learning for user-behavior analysis on a dataset of over 180,000 images.
    \item Implemented data preprocessing pipelines and feature extraction algorithms for behavioral pattern recognition.
    \item Developed automated data labeling systems and active learning strategies to improve model performance iteratively.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/Diary-with-ChatGPT-Comment}{\uline{
\textbf{Diary with AI Feedback}}} \hfill Sep 2023 -- On Going
\begin{itemize}[leftmargin=0.2in]
    \item Designed and implemented a journaling program integrated with OpenAI's GPT API, generating insightful feedback for over 750 diary entries.
    \item Developed a diary sorting algorithm to retrieve contextually similar past entries by vector search, maintaining API costs below \$0.2 per call.
    \item Implemented semantic similarity search using embeddings and cosine similarity for content recommendation.
    \item Optimized data-sorting pipelines and API request processes, reducing average diary load time from 10s to 0.5s.
    \item Built natural language processing workflows for sentiment analysis and topic modeling of diary content.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://chengyongkang.me/chat}{\uline{
\textbf{Self-Clone Chatbot with Diary Database}}} \hfill Oct 2024 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a self-hosted AI-powered chatbot that replicates personal interaction styles using fine-tuned language models.
    \item Integrated OpenAI API and a NoSQL database for real-time Q\&A functionality with personal diary data.
    \item Implemented retrieval-augmented generation (RAG) architecture for contextually relevant responses.
    \item Developed custom tokenization and embedding strategies for personal writing style mimicry.
    \item Created evaluation metrics and A/B testing frameworks to measure chatbot response quality and user satisfaction.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/walrus_test}{\uline{
\textbf{Fourier Epicycle Drawing Visualization System}}} \hfill May 2025
\begin{itemize}[leftmargin=0.2in]
    \item Built an interactive Python/Pygame app to draw strokes and visualize their Fourier decomposition as animated epicycles.
    \item Implemented stroke preprocessing (merging, equidistant resampling) for accurate Fourier analysis.
    \item Developed mathematical algorithms for discrete Fourier transform and complex number manipulation.
    \item Created real-time visualization of mathematical concepts with interactive parameter adjustment.
    \item Designed modular utilities for signal processing, mathematical visualization, and educational demonstrations.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/utek_disaster_communication_system}{\uline{
\textbf{UTEK Wildfire Disaster Communication System}}} \hfill Jan 2025
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Top 8 Finalist} in University of Toronto Engineering Competition (UTEK) among all competing teams.
    \item Created severity classification system with automated risk assessment using machine learning algorithms.
    \item Implemented geospatial analysis and clustering algorithms for intelligent resource allocation.
    \item Built predictive models for wildfire spread patterns using historical data and environmental factors.
    \item Developed image recognition systems for automated fire detection from uploaded photos.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/XiuShw/Wrong-Tree}{\uline{
\textbf{Core AI Developer, Wrong-Tree Unity Game}}} \hfill Dec 2024 - Jan 2025
\begin{itemize}[leftmargin=0.2in]
    \item Designed 9-state finite state machine (Idle, Wander, Share, Steal, Flee) for intelligent NPC behaviors.
    \item Implemented reinforcement learning algorithms with proximity detection and dynamic reputation scoring.
    \item Created multi-agent systems supporting simultaneous interactions with emergent social behaviors.
    \item Built utility-based AI systems with decision trees and behavior trees for complex NPC decision-making.
    \item Developed machine learning models for adaptive NPC behavior based on player interaction patterns.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{City Mapify – Interactive City Mapping Application (University of Toronto)} \hfill Jan 2025 - Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Implemented advanced pathfinding algorithms (\textbf{Dijkstra, A*, Simulated Annealing, Ant Colony Optimization}) for route optimization.
    \item Developed machine learning models for traffic pattern prediction and dynamic route recommendation.
    \item Built optimization algorithms using genetic algorithms and swarm intelligence for delivery route planning.
    \item Created data visualization systems for real-time traffic analysis and route performance metrics.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{Computer Vision for Medical Image Analysis} \hfill Academic Project
\begin{itemize}[leftmargin=0.2in]
    \item Developed CNN architectures for medical image segmentation and classification tasks.
    \item Implemented data augmentation strategies and transfer learning from pre-trained models.
    \item Achieved 92\% accuracy on medical image classification using ResNet and DenseNet architectures.
    \item Built automated preprocessing pipelines for DICOM image standardization and normalization.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% AWARDS & ACCOMPLISHMENTS
%------------------------------------------
\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\noindent\textbf{University of Toronto Excellence Award (UTEA)} \hfill Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Awarded UTEA for top academic performance and research potential in machine learning applications.
    \item Completed a 14-week full-time research project with faculty supervision focusing on AI/ML systems.
    \item Received \$7,500 scholarship for research excellence and inclusion.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for outstanding academic performance in machine learning and data science courses.
\end{itemize}

\end{document}