\documentclass[letterpaper,10pt]{article}
\usepackage{geometry}
\geometry{margin=0.7in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\pagenumbering{gobble}

\setlength{\parskip}{0.5pt}
\setlist{nosep}  
\usepackage[compact]{titlesec}
\usepackage{setspace}
\setstretch{1.0}

\begin{document}

%------------------------------------------
% HEADER
%------------------------------------------
\begin{center}
    \huge \textbf{Yongkang Cheng}\\
    \vspace{0.2cm}
    \small
    \href{https://chengyongkang.me/}{\uline{chengyongkang.me}} \,\textbar{}\,
    437-663-2855 \,\textbar{}\,
    \href{https://www.github.com/Ken-2511/}{\uline{github.com/Ken-2511}} \,\textbar{}\,
    \href{mailto:iwmain@outlook.com}{\uline{iwmain@outlook.com}} \,\textbar{}\,
    \href{https://www.linkedin.com/in/chengyongkang/}{\uline{linkedin.com/in/chengyongkang}}
\end{center}

\vskip -2ex
\noindent\rule{\linewidth}{2pt}

%------------------------------------------
% EDUCATION
%------------------------------------------
\section*{\textbf{EDUCATION}}
\textbf{University of Toronto (St. George Campus), Toronto, ON} \hfill Sep 2023 - May 2028 (expected)\\
Bachelor of Applied Science in Computer Engineering + PEY Co-op (cGPA: 3.87/4.0) \\
Relevant Courses: Applied Fundamentals of Deep Learning, Software Design and Communication

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% TECHNICAL SKILLS
%------------------------------------------
\section*{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Programming:} Python, C/C++, Node.js, Java, JavaScript, TypeScript
    \item \textbf{Web \& Backend:} React, FastAPI, Node.js, Nginx, Docker, SQL/NoSQL, RESTful APIs
    \item \textbf{AI \& Data:} PyTorch, LangChain, NumPy, Pandas, Matplotlib, OpenAI API
    \item \textbf{Tools \& Platforms:} Git, SSH, Linux, Firebase, libcurl, OpenMP, Streamlit, Flask
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% EXPERIENCE
%------------------------------------------
\section*{\textbf{EXPERIENCE}}

\noindent\href{https://volun-track.web.app}{\uline{
\textbf{Frontend Manager, Voluntrack.org (Non-Profit)}}} \textit{React, Figma, MS Project} \hfill May 2024 - Present\\
\textit{Volunteer, Voluntrack.org} \hfill \textit{Remote}
\begin{itemize}[leftmargin=0.2in]
    \item Led a 4-person team to redesign the web interface using React.js, improving user engagement by 20\%.
    \item Designed UI in Figma and managed tasks with GitHub Project.
    \item Integrated Firebase for secure volunteer data storage and real-time search, allowing fuzzy search and filtering.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/ppm-psk-visualize}
{\uline{\textbf{Research Assistant, Ultra-Wideband Receiver Design (University of Toronto)}}} \hfill Jun 2025 - Jul 2025\\
\textit{Research Intern, X-Lab, University of Toronto} \hfill \textit{Toronto, ON}
\begin{itemize}[leftmargin=0.2in]
    \item Built Python/Simulink pipelines for 2ns symbol sync and carrier recovery under discontinuous 4GHz.
    \item Developed pulse-position detection and K-means cluster calibration algorithms to mitigate timing shifts.
    \item Presented at Undergraduate Engineering Research Day with an interactive hybrid-modulation demo site.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% PROJECTS
%------------------------------------------
\section*{\textbf{PROJECTS}}

\noindent\href{https://github.com/Ken-2511/utek_disaster_communication_system}{\uline{
\textbf{UTEK Wildfire Disaster Communication System}}} \hfill Jan 2025
\begin{itemize}[leftmargin=0.2in]
    \item \textbf{Top 8 Finalist} in University of Toronto Engineering Competition (UTEK) among all competing teams.
    \item Built real-time communication platform with Python, Streamlit, and Flask for wildfire emergency response coordination.
    \item Implemented interactive map interface using Folium for visualizing fire incidents and location-based alerts.
    \item Developed bidirectional communication system between residents and rescue teams with photo upload capabilities.
    \item Created severity classification system with automated risk assessment for intelligent resource allocation.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{City Mapify – Interactive City Mapping Application (University of Toronto)} \hfill Jan 2025 - Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Developed a high-performance mapping engine in C++ to process OpenStreetMap data and render city maps.
    \item Designed efficient spatial data structures (\textbf{quadtrees}) for dynamic querying and smooth zoom-based rendering.
    \item Implemented advanced pathfinding algorithms (\textbf{Dijkstra, A*, Simulated Annealing}) for route planning and delivery optimization.
    \item Enhanced performance with multithreading (OpenMP) and RESTful API integration (libcurl).
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/HandwritingRecognition}{\uline{
\textbf{Project Lead, Handwritten Text Recognition (University of Toronto)}}} \hfill Jun 2024 - Aug 2024
\begin{itemize}[leftmargin=0.2in]
    \item Led a remote team to develop a PyTorch-based CRNN model for handwritten text recognition.
    \item Achieved 87\% word-level and 95\% character-level accuracy on the test set with 10,000+ samples.
    \item Deployed connected-pixel algorithms for word positioning and word segmentation, processing 1024$\times$1024 images in less than 4 seconds.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://chengyongkang.me/chat}{\uline{
\textbf{Self-Clone Chatbot with Diary Database}}} \hfill Oct 2024 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a self-hosted AI-powered chatbot that replicates personal interaction styles, deployed using React.js, FastAPI, and Nginx on a Raspberry Pi.
    \item Integrated OpenAI API and a NoSQL database for real-time Q\&A functionality with personal diary data.
    \item Ensured secure and seamless remote access by implementing TLS encryption, DDNS, and optimizing for daily traffic.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/Diary-with-ChatGPT-Comment}{\uline{
\textbf{Diary with AI Feedback}}} \hfill Sep 2023 -- On Going
\begin{itemize}[leftmargin=0.2in]
    \item Designed and implemented a journaling program integrated with OpenAI's GPT API, generating insightful feedback for over 750 diary entries.
    \item Developed a diary sorting algorithm to retrieve contextually similar past entries by vector search, maintaining API costs below \$0.2 per call.
    \item Optimized data-sorting pipelines and API request processes, reducing average diary load time from 10s to 0.5s.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/WillPower}{\uline{
\textbf{WillPower \textbar{} Time Management \& Monitoring}}} \hfill Jan 2025 - Present
\begin{itemize}[leftmargin=0.2in]
    \item Built a modular system with Raspberry Pi capturing images and sending them to a Windows host for local storage and analysis.
    \item Deployed Nginx, FastAPI, and libcurl for data transfer, facilitating real-time user monitoring and minimal downtime.
    \item Currently exploring Azure Face APIs and transfer learning for user-behavior analysis on a dataset of over 180,000 images.
\end{itemize}

\vspace{0.2cm}
\noindent\href{https://github.com/Ken-2511/AcornCarwler}{\uline{
\textbf{Acorn Course Timetable Monitor Crawler}}} \hfill Personal Project
\begin{itemize}[leftmargin=0.2in]
    \item Built automated Python web crawler to monitor University of Toronto's Acorn course timetable system for real-time changes.
    \item Implemented intelligent change detection algorithms with robust error handling and automatic recovery mechanisms.
    \item Developed notification system for course availability updates, helping students secure spots in full courses.
\end{itemize}

\noindent\rule{\linewidth}{1pt}

%------------------------------------------
% AWARDS & ACCOMPLISHMENTS
%------------------------------------------
\section*{\textbf{AWARDS \& ACCOMPLISHMENTS}}

\noindent\textbf{University of Toronto Excellence Award (UTEA)} \hfill Apr 2025
\begin{itemize}[leftmargin=0.2in]
    \item Awarded UTEA for top academic performance and research potential.
    \item Received \$7,500 scholarship for research excellence and inclusion.
\end{itemize}

\vspace{0.2cm}
\noindent\textbf{ECE Awards \& Dean's List Scholar (UofT)} \hfill Sep 2024
\begin{itemize}[leftmargin=0.2in]
    \item Recognized for outstanding academic performance.
\end{itemize}

\end{document}